A neural coarse graining theory of consciousness

### 2018-05-31 Paper_neural_coarse_graining_of_consciousness.tex
Overleaf Test

				@ It seems true that we cannot consciously access information at all scale. We can only be aware of information processed at a certain level of coarse-graining in the neural system.

				@ Information processing of individual neurons are highly noisy. Neurons fires all the time. However, those massive action potentials do not appear in our conscious contents.

				@ Don't even mention ion channel dynamic.

>>>>

				@ It seems true that we cannot consciously access information processed at all scale in the neural system. Only information at a certain level of coarse-graining is able to become parts of conscious contents.

				@ When we focus on microscopic level of the neural system, information processing in individual neurons is highly noisy and state transitions of neurons are stochastic \citep{Goldwyn2011, White2000}. However, instead of seeing action potentials and random noise at microscopic levels, conscious contents shows astonishing stability and robustness against to noise in the neural system \citep{mathis1995computational}.

				 Neurons fires all the time. However, those massive action potentials do not appear in our conscious contents.
